---
title: "Section: Empirical analysis"
output: html_notebook
---

```{r message=FALSE, warning=FALSE}
library(dplyr)
library(tidyr)
library(ggplot2)
library(readxl)
library(lubridate)
library(urca)
library(tseries)
library(seasonal)
library(lmtest)
library(vars)
library(forecast)
library(graphics)
library(Hmisc)
library(xtable)
library(stargazer)

# Theming

theme_set(
  theme_bw(base_size = 10) +
    theme(
      plot.title = element_text(size = 14,
                                margin = margin(0, 0, 4, 0, "pt")),
      plot.subtitle = element_text(size = 8),
      plot.caption = element_text(size = 6),
      panel.border = element_blank()
    )
)

rm(list=ls())

col <- rcartocolor::carto_pal(12, "Bold")
source("func/helper_functions.R")

# Load Data
sales <- read_excel("../data/sales.xls")
ads <- read_excel("../data/ads.xls")
adprice <- read_excel("../data/adprice.xls")

#combine the dataframes
df <- sales %>%
  dplyr::select(-Status) %>%
  left_join(., ads %>%
              dplyr::select(- Status), 
            by = c("Titel","Heft Nr.")) %>%
  left_join(., adprice %>%
              dplyr::select(-Status),
            by = c("Titel","Heft Nr.")) %>%
  mutate(year = as.numeric(substrRight(`Heft Nr.`, 4)),
         issue = as.numeric(substr(`Heft Nr.`,1,2)))
```

```{r}
ggplot(df, aes(Gattung)) +
  geom_bar(fill = col[2], alpha = 0.8) +
  coord_flip()
```

```{r}
df %>%
  filter(Gattung == "Aktuelle Zeitschriften und Magazine") %>%
  ggplot(aes(Titel)) +
  geom_bar(fill = col[3], alpha = 0.8) +
  coord_flip()
```

We use the cross correlation function (CCF) to estimate the relationship between two time series ($y_t$ and $x_t$). However, one difficulty is that the CCF is affected by the time series structure of the x-variable and any “in common” trends the $x$ and $y$ series may have over time.

One strategy for dealing with this difficulty is called “pre-whitening.”  The steps are:

  1) Determine a time series model for the x-variable and store the residuals from this model.

  2) Filter the y-variable series using the x-variable model (using the estimated coefficients from step 1). In this step we find differences between observed y-values and “estimated” y-values based on the x-variable model.

  3) Examine the CCF between the residuals from Step 1 and the filtered y-values from Step 2.  This CCF can be used to identify the possible terms for a lagged regression.
  
This strategy stems from the fact that when the input series (say, wt) is “white noise” the patterns of the CCF between wt and zt, a linear combination of lags of the wt, are easily identifiable (and easily derived).  Step 1 above creates a “white noise” series as the input.  Conceptually, Step 2 above arises from a starting point that y-series = linear combination of x-series.  If we “transform” the x-series to white noise (residuals from its ARIMA model) then we should apply the transformation to both sides of the equation to preserve an equality of sorts.

# 1. FOCUS, Der Spiegel, Stern

```{r}
keep <- c("Der Spiegel","FOCUS","Stern")

fss <- df %>%
  filter(Titel %in% keep) %>%
  mutate(date = calculate_week(issue, year))
```

```{r}
ggplot(fss, aes(date, `Verkauf Gesamt`/1000,
                color=Titel)) +
  geom_line() +
  scale_color_manual(values = col[1:3]) +
  labs(x="", color="", title = NULL, y="Sales in tsd.") +
  scale_x_date(date_breaks = "years" , date_labels = "%Y") +
  geom_vline(xintercept = as.numeric(as.Date("2004-08-18")), linetype = "dashed", lwd=.5) +
  geom_vline(xintercept = as.numeric(as.Date("2006-08-18")), linetype = "dashed", lwd=.5) +
  geom_vline(xintercept = as.numeric(as.Date("2013-08-18")), linetype = "dashed", lwd=.5) +
  geom_vline(xintercept = as.numeric(as.Date("2015-08-18")), linetype = "dashed", lwd=.5) +
  theme(legend.position="bottom")
  

ggsave('../figs/sales_fss.png', width = 8, height = 6)
```

```{r}
ggplot(fss, aes(date, `Anzeigen Gesamt`,
                color=Titel)) +
  geom_line() +
  scale_color_manual(values = col[1:3]) +
  labs(x="", color="", title = NULL, y="Total advertising pages") +
  scale_x_date(date_breaks = "years" , date_labels = "%Y") +
  geom_vline(xintercept = as.numeric(as.Date("2004-08-18")), linetype = "dashed", lwd=.5) +
  geom_vline(xintercept = as.numeric(as.Date("2006-08-18")), linetype = "dashed", lwd=.5) +
  geom_vline(xintercept = as.numeric(as.Date("2013-08-18")), linetype = "dashed", lwd=.5) +
  geom_vline(xintercept = as.numeric(as.Date("2015-08-18")), linetype = "dashed", lwd=.5) +
  theme(legend.position="bottom")

ggsave('../figs/ads_fss.png', width = 8, height = 6)
```

## FSS - Sample 1
```{r}
# time period 1
min <- calculate_week(33, 2004)
max <- calculate_week(33, 2006)
```

### Sales
```{r fss_sales1: Create df}
fss %>%
  dplyr::select(`Verkauf Gesamt`, date, Titel) %>%
  spread(Titel, `Verkauf Gesamt`) %>%
  filter(date >= as.Date(min)) %>%
  filter(date <= as.Date(max)) %>%
  dplyr::select(-date) -> tempdf
```
  
```{r fss_sales1: Calculate Arima}
results <- list()
mag <- names(tempdf)
x <- 1

for (i in mag) {
    selected <- tempdf[, -which(names(tempdf) == i)]
    xreg_matrix <- as.matrix(cbind(selected[,1],selected[,2]))
    temp <- auto.arima(tempdf[,i], xreg = xreg_matrix)
    
    results[[x]] <- temp
    x <- x+1
  }

resid <- cbind(results[[1]]$residuals, results[[2]]$residuals, results[[3]]$residuals)
```

```{r fss_sales1: Plot residuals}
autoplot(resid) +
  scale_color_manual(labels = mag, values = col[1:3]) +
  geom_hline(yintercept = 0, color = "grey50") +
  labs(y="residuals", x="", color = "",
       caption = paste("Timespan:", min,"to", max)) +
  theme(legend.position = "bottom")

ggsave("../figs/arima_circ_fss1.png", width = 8, height = 6)
```

```{r fss_sales1: Calculate CCF}
corr_temp <- resid %>% as.data.frame()
names(corr_temp) <- mag

# Create empty matrix
corr <- expand.grid(names(corr_temp), names(corr_temp))

corr$`-3` <- NA
corr$`-2` <- NA
corr$`-1` <- NA
corr$`0` <- NA
corr$`1` <- NA
corr$`2` <- NA
corr$`3` <- NA
  
x <- 1
  
for (corr1Id in 1:ncol(corr_temp)) {
    c1 = corr_temp[,corr1Id]

    for(corr2Id in 1:ncol(corr_temp)) {
      c2 = corr_temp[,corr2Id]
      correlation = ccf(c1, c2, lag.max = 3, 
                        na.action = na.contiguous,
                        plot=F)
      
      corr[x,3:9] <- correlation$acf %>% 
        as.data.frame() %>% t()
    
      x<- x+1
    }
}
```

```{r fss_sales1: CCF long df}
# convert dataframe to long format
corrLong_fss_sales1 <- corr %>%
    gather(lag, ccf, `-3`:`3`) %>%
  mutate(lag = as.numeric(lag),
         type = "sales",
         sample = "news magazines (1)")
```

```{r fss_sales1: Plot CCF}
# Calculate confidence intervals
ci_upper <- 2/sqrt(length(resid[,1]))
ci_lower <- -2/sqrt(length(resid[,1]))

corrLong_fss_sales1 %>%
  filter(Var1!=Var2) %>%
  ggplot(aes(lag,ccf,
             fill=Var1)) +
  geom_col(position = "dodge",
           #show.legend = F,
           alpha=0.8) +
  scale_fill_manual(values=col) +
  facet_wrap(~Var2, ncol=3)+
  scale_x_continuous(breaks = c(-3:3)) +
  scale_y_continuous(
    limits = c(-0.7,0.7),
    breaks = seq(-0.7,0.7,0.2)) +
  geom_hline(yintercept = ci_upper, 
             color = "black",
             size = 0.3,
             linetype = 2)+
  geom_hline(yintercept = ci_lower, 
             color = "black",
             size=0.3,
             linetype = 2)+
  labs(x="", fill="", caption = paste("Timespan:", min,"to", max)) +
  theme(legend.position = "bottom")

ggsave("../figs/ccf_sales_fss1.png", width = 8, height = 6)
```

### Advertising
```{r fss_ads1: Create df}
fss %>%
  dplyr::select(`Anzeigen Gesamt`, date, Titel) %>%
  spread(Titel, `Anzeigen Gesamt`) %>%
  filter(date >= as.Date(min)) %>%
  filter(date <= as.Date(max)) %>%
  dplyr::select(-date) -> tempdf
```
  
```{r fss_ads1: Calculate Arima}
results <- list()
mag <- names(tempdf)
x <- 1

for (i in mag) {
    selected <- tempdf[, -which(names(tempdf) == i)]
    xreg_matrix <- as.matrix(cbind(selected[,1],selected[,2]))
    temp <- auto.arima(tempdf[,i], xreg = xreg_matrix)
    
    results[[x]] <- temp
    x <- x+1
  }

resid <- cbind(results[[1]]$residuals, results[[2]]$residuals, results[[3]]$residuals)
```

```{r fss_ads1: Plot residuals}
autoplot(resid) +
  scale_color_manual(labels = mag, values = col[1:3]) +
  geom_hline(yintercept = 0, color = "grey50") +
  labs(y="residuals", x="", color = "",
       caption = paste("Timespan:", min,"to", max)) +
  theme(legend.position = "bottom")

ggsave("../figs/arima_ads_fss1.png", width = 8, height = 6)
```

```{r fss_ads1: Calculate CCF}
corr_temp <- resid %>% as.data.frame()
names(corr_temp) <- mag

# Create empty matrix
corr <- expand.grid(names(corr_temp), names(corr_temp))

corr$`-3` <- NA
corr$`-2` <- NA
corr$`-1` <- NA
corr$`0` <- NA
corr$`1` <- NA
corr$`2` <- NA
corr$`3` <- NA
  
x <- 1
  
for (corr1Id in 1:ncol(corr_temp)) {
    c1 = corr_temp[,corr1Id]

    for(corr2Id in 1:ncol(corr_temp)) {
      c2 = corr_temp[,corr2Id]
      correlation = ccf(c1, c2, lag.max = 3, 
                        na.action = na.contiguous,
                        plot=F)
      
      corr[x,3:9] <- correlation$acf %>% 
        as.data.frame() %>% t()
    
      x<- x+1
    }
}
```

```{r fss_ads1: CCF long df}
# convert dataframe to long format
corrLong_fss_ads1 <- corr %>%
    gather(lag, ccf, `-3`:`3`) %>%
  mutate(lag = as.numeric(lag),
         type = "ads",
         sample = "news magazines (1)")
```

```{r fss_ads1: Plot CCF}
# Calculate confidence intervals
ci_upper <- 2/sqrt(length(resid[,1]))
ci_lower <- -2/sqrt(length(resid[,1]))

corrLong_fss_ads1 %>%
  filter(Var1!=Var2) %>%
  ggplot(aes(lag,ccf,
             fill=Var1)) +
  geom_col(position = "dodge",
           #show.legend = F,
           alpha=0.8) +
  scale_fill_manual(values=col) +
  facet_wrap(~Var2, ncol=3)+
  scale_x_continuous(breaks = c(-3:3)) +
  scale_y_continuous(
    limits = c(-0.7,0.7),
    breaks = seq(-0.7,0.7,0.2)) +
  geom_hline(yintercept = ci_upper, 
             color = "black",
             size = 0.3,
             linetype = 2)+
  geom_hline(yintercept = ci_lower, 
             color = "black",
             size=0.3,
             linetype = 2)+
  labs(x="", fill="", caption = paste("Timespan:", min,"to", max)) +
  theme(legend.position = "bottom")

ggsave("../figs/ccf_ads_fss1.png", width = 8, height = 6)
```

## FSS - Sample 2
```{r}
# time period 2
min <- calculate_week(33, 2013)
max <- calculate_week(33, 2015)
```

### Sales
```{r fss_sales2: Create df}
fss %>%
  dplyr::select(`Verkauf Gesamt`, date, Titel) %>%
  spread(Titel, `Verkauf Gesamt`) %>%
  filter(date >= as.Date(min)) %>%
  filter(date <= as.Date(max)) %>%
  dplyr::select(-date) -> tempdf
```
  
```{r fss_sales2: Calculate Arima}
results <- list()
mag <- names(tempdf)
x <- 1

for (i in mag) {
    selected <- tempdf[, -which(names(tempdf) == i)]
    xreg_matrix <- as.matrix(cbind(selected[,1],selected[,2]))
    temp <- auto.arima(tempdf[,i], xreg = xreg_matrix)
    
    results[[x]] <- temp
    x <- x+1
  }

resid <- cbind(results[[1]]$residuals, results[[2]]$residuals, results[[3]]$residuals)
```

```{r fss_sales2: Plot residuals}
autoplot(resid) +
  scale_color_manual(labels = mag, values = col[1:3]) +
  geom_hline(yintercept = 0, color = "grey50") +
  labs(y="residuals", x="", color = "",
       caption = paste("Timespan:", min,"to", max)) +
  theme(legend.position = "bottom")

ggsave("../figs/arima_circ_fss2.png", width = 8, height = 6)
```

```{r fss_sales2: Calculate CCF}
corr_temp <- resid %>% as.data.frame()
names(corr_temp) <- mag

# Create empty matrix
corr <- expand.grid(names(corr_temp), names(corr_temp))

corr$`-3` <- NA
corr$`-2` <- NA
corr$`-1` <- NA
corr$`0` <- NA
corr$`1` <- NA
corr$`2` <- NA
corr$`3` <- NA
  
x <- 1
  
for (corr1Id in 1:ncol(corr_temp)) {
    c1 = corr_temp[,corr1Id]

    for(corr2Id in 1:ncol(corr_temp)) {
      c2 = corr_temp[,corr2Id]
      correlation = ccf(c1, c2, lag.max = 3, 
                        na.action = na.contiguous,
                        plot=F)
      
      corr[x,3:9] <- correlation$acf %>% 
        as.data.frame() %>% t()
    
      x<- x+1
    }
}
```

```{r fss_sales2: CCF long df}
# convert dataframe to long format
corrLong_fss_sales2 <- corr %>%
    gather(lag, ccf, `-3`:`3`) %>%
  mutate(lag = as.numeric(lag),
         type = "sales",
         sample = "news magazines (2)")
```

```{r fss_sales2: Plot CCF}
# Calculate confidence intervals
ci_upper <- 2/sqrt(length(resid[,1]))
ci_lower <- -2/sqrt(length(resid[,1]))

corrLong_fss_sales2 %>%
  filter(Var1!=Var2) %>%
  ggplot(aes(lag,ccf,
             fill=Var1)) +
  geom_col(position = "dodge",
           #show.legend = F,
           alpha=0.8) +
  scale_fill_manual(values=col) +
  facet_wrap(~Var2, ncol=3)+
  scale_x_continuous(breaks = c(-3:3)) +
  scale_y_continuous(
    limits = c(-0.7,0.7),
    breaks = seq(-0.7,0.7,0.2)) +
  geom_hline(yintercept = ci_upper, 
             color = "black",
             size = 0.3,
             linetype = 2)+
  geom_hline(yintercept = ci_lower, 
             color = "black",
             size=0.3,
             linetype = 2)+
  labs(x="", fill="", caption = paste("Timespan:", min,"to", max)) +
  theme(legend.position = "bottom")

ggsave("../figs/ccf_sales_fss2.png", width = 8, height = 6)
```

### Advertising
```{r fss_ads2: Create df}
fss %>%
  dplyr::select(`Anzeigen Gesamt`, date, Titel) %>%
  spread(Titel, `Anzeigen Gesamt`) %>%
  filter(date >= as.Date(min)) %>%
  filter(date <= as.Date(max)) %>%
  dplyr::select(-date) -> tempdf
```
  
```{r fss_ads2: Calculate Arima}
results <- list()
mag <- names(tempdf)
x <- 1

for (i in mag) {
    selected <- tempdf[, -which(names(tempdf) == i)]
    xreg_matrix <- as.matrix(cbind(selected[,1],selected[,2]))
    temp <- auto.arima(tempdf[,i], xreg = xreg_matrix)
    
    results[[x]] <- temp
    x <- x+1
  }

resid <- cbind(results[[1]]$residuals, results[[2]]$residuals, results[[3]]$residuals)
```

```{r fss_ads2: Plot residuals}
autoplot(resid) +
  scale_color_manual(labels = mag, values = col[1:3]) +
  geom_hline(yintercept = 0, color = "grey50") +
  labs(y="residuals", x="", color = "",
       caption = paste("Timespan:", min,"to", max)) +
  theme(legend.position = "bottom")

ggsave("../figs/arima_ads_fss2.png", width = 8, height = 6)
```

```{r fss_ads2: Calculate CCF}
corr_temp <- resid %>% as.data.frame()
names(corr_temp) <- mag

# Create empty matrix
corr <- expand.grid(names(corr_temp), names(corr_temp))

corr$`-3` <- NA
corr$`-2` <- NA
corr$`-1` <- NA
corr$`0` <- NA
corr$`1` <- NA
corr$`2` <- NA
corr$`3` <- NA
  
x <- 1
  
for (corr1Id in 1:ncol(corr_temp)) {
    c1 = corr_temp[,corr1Id]

    for(corr2Id in 1:ncol(corr_temp)) {
      c2 = corr_temp[,corr2Id]
      correlation = ccf(c1, c2, lag.max = 3, 
                        na.action = na.contiguous,
                        plot=F)
      
      corr[x,3:9] <- correlation$acf %>% 
        as.data.frame() %>% t()
    
      x<- x+1
    }
}
```

```{r fss_ads2: CCF long df}
# convert dataframe to long format
corrLong_fss_ads2 <- corr %>%
    gather(lag, ccf, `-3`:`3`) %>%
  mutate(lag = as.numeric(lag),
         type = "ads",
         sample = "news magazines (2)")
```

```{r fss_ads2: Plot CCF}
# Calculate confidence intervals
ci_upper <- 2/sqrt(length(resid[,1]))
ci_lower <- -2/sqrt(length(resid[,1]))

corrLong_fss_ads2 %>%
  filter(Var1!=Var2) %>%
  ggplot(aes(lag,ccf,
             fill=Var1)) +
  geom_col(position = "dodge",
           #show.legend = F,
           alpha=0.8) +
  scale_fill_manual(values=col) +
  facet_wrap(~Var2, ncol=3)+
  scale_x_continuous(breaks = c(-3:3)) +
  scale_y_continuous(
    limits = c(-0.7,0.7),
    breaks = seq(-0.7,0.7,0.2)) +
  geom_hline(yintercept = ci_upper, 
             color = "black",
             size = 0.3,
             linetype = 2)+
  geom_hline(yintercept = ci_lower, 
             color = "black",
             size=0.3,
             linetype = 2)+
  labs(x="", fill="", caption = paste("Timespan:", min,"to", max)) +
  theme(legend.position = "bottom")

ggsave("../figs/ccf_ads_fss2.png", width = 8, height = 6)
```

# 2. TV
```{r}
keep <- c("TV Movie", "TV Spielfilm", "TV Today")

min <- calculate_biweek(15, 2007)
max <- calculate_biweek(15, 2011)

tv <- df %>%
  filter(Titel %in% keep) %>%
  mutate(date = calculate_biweek(issue, year))
```

```{r}
ggplot(tv, aes(date, `Verkauf Gesamt`/1000,
                color=Titel)) +
  geom_line() +
  scale_color_manual(values = col[1:3]) +
  scale_x_date(date_breaks = "1 year", date_labels = "%Y") +
  labs(x="", color="", title = NULL, y="Sales in tsd.") +
  geom_vline(xintercept = as.numeric(min), linetype = "dashed", lwd=.5) +
  geom_vline(xintercept = as.numeric(max), linetype = "dashed", lwd=.5) +
  theme(legend.position="bottom")
  

ggsave('../figs/sales_tv.png', width = 8, height = 6)
```

```{r}
ggplot(tv, aes(date, `Anzeigen Gesamt`,
                color=Titel)) +
  geom_line() +
  scale_color_manual(values = col[1:3]) +
  labs(x="", color="", title = NULL, y="Total advertising pages") +
  scale_x_date(date_breaks = "years" , date_labels = "%Y") +
  geom_vline(xintercept = as.numeric(min), linetype = "dashed", lwd=.5) +
  geom_vline(xintercept = as.numeric(max), linetype = "dashed", lwd=.5) +
  theme(legend.position="bottom")

ggsave('../figs/ads_tv.png', width = 8, height = 6)
```

## Sales
```{r tv_sales: Create df}
tv %>%
  dplyr::select(`Verkauf Gesamt`, date, Titel) %>%
  spread(Titel, `Verkauf Gesamt`) %>%
  filter(date >= as.Date(min)) %>%
  filter(date <= as.Date(max)) %>%
  dplyr::select(-date) -> tempdf
```
  
```{r tv_sales: Calculate Arima}
results <- list()
mag <- names(tempdf)
x <- 1

for (i in mag) {
    selected <- tempdf[, -which(names(tempdf) == i)]
    xreg_matrix <- as.matrix(cbind(selected[,1],selected[,2]))
    temp <- auto.arima(tempdf[,i], xreg = xreg_matrix)
    
    results[[x]] <- temp
    x <- x+1
  }

resid <- cbind(results[[1]]$residuals, results[[2]]$residuals, results[[3]]$residuals)
```

```{r tv_sales: Plot residuals}
autoplot(resid) +
  scale_color_manual(labels = mag, values = col[1:3]) +
  geom_hline(yintercept = 0, color = "grey50") +
  labs(y="residuals", x="", color = "",
       caption = paste("Timespan:", min,"to", max)) +
  theme(legend.position = "bottom")

ggsave("../figs/arima_sales_tv.png", width = 8, height = 6)
```

```{r tv_sales: Calculate CCF}
corr_temp <- resid %>% as.data.frame()
names(corr_temp) <- mag

# Create empty matrix
corr <- expand.grid(names(corr_temp), names(corr_temp))

corr$`-3` <- NA
corr$`-2` <- NA
corr$`-1` <- NA
corr$`0` <- NA
corr$`1` <- NA
corr$`2` <- NA
corr$`3` <- NA
  
x <- 1
  
for (corr1Id in 1:ncol(corr_temp)) {
    c1 = corr_temp[,corr1Id]

    for(corr2Id in 1:ncol(corr_temp)) {
      c2 = corr_temp[,corr2Id]
      correlation = ccf(c1, c2, lag.max = 3, 
                        na.action = na.contiguous,
                        plot=F)
      
      corr[x,3:9] <- correlation$acf %>% 
        as.data.frame() %>% t()
    
      x<- x+1
    }
}
```

```{r ty_sales; CCF long df}
# convert dataframe to long format
corrLong_tv_sales <- corr %>%
    gather(lag, ccf, `-3`:`3`) %>%
  mutate(lag = as.numeric(lag),
         type = "sales",
         sample = "program guides")
```

```{r tv_sales: Plot CCF}
# Calculate confidence intervals
ci_upper <- 2/sqrt(length(resid[,1]))
ci_lower <- -2/sqrt(length(resid[,1]))

corrLong_tv_sales %>%
  filter(Var1!=Var2) %>%
  ggplot(aes(lag,ccf,
             fill=Var1)) +
  geom_col(position = "dodge",
           #show.legend = F,
           alpha=0.8) +
  scale_fill_manual(values=col) +
  facet_wrap(~Var2, ncol=3)+
  scale_x_continuous(breaks = c(-3:3)) +
  scale_y_continuous(
    limits = c(-1,1),
    breaks = seq(-1,1,0.2)) +
  geom_hline(yintercept = ci_upper, 
             color = "black",
             size = 0.3,
             linetype = 2)+
  geom_hline(yintercept = ci_lower, 
             color = "black",
             size=0.3,
             linetype = 2)+
  labs(x="", fill="", caption = paste("Timespan:", min,"to", max)) +
  theme(legend.position = "bottom")

ggsave("../figs/ccf_sales_tv.png", width = 8, height = 6)
```

## Advertising
```{r tv_ads: Create df}
tv %>%
  dplyr::select(`Anzeigen Gesamt`, date, Titel) %>%
  spread(Titel, `Anzeigen Gesamt`) %>%
  filter(date >= as.Date(min)) %>%
  filter(date <= as.Date(max)) %>%
  dplyr::select(-date) -> tempdf
```
  
```{r tv_ads: Calculate Arima}
results <- list()
mag <- names(tempdf)
x <- 1

for (i in mag) {
    selected <- tempdf[, -which(names(tempdf) == i)]
    xreg_matrix <- as.matrix(cbind(selected[,1],selected[,2]))
    temp <- auto.arima(tempdf[,i], xreg = xreg_matrix)
    
    results[[x]] <- temp
    x <- x+1
  }

resid <- cbind(results[[1]]$residuals, results[[2]]$residuals, results[[3]]$residuals)
```

```{r tv_ads: Plot residuals}
autoplot(resid) +
  scale_color_manual(labels = mag, values = col[1:3]) +
  geom_hline(yintercept = 0, color = "grey50") +
  labs(y="residuals", x="", color = "",
       caption = paste("Timespan:", min,"to", max)) +
  theme(legend.position = "bottom")

ggsave("../figs/arima_ads_tv.png", width = 8, height = 6)
```

```{r tv_ads: Calculate CCF}
corr_temp <- resid %>% as.data.frame()
names(corr_temp) <- mag

# Create empty matrix
corr <- expand.grid(names(corr_temp), names(corr_temp))

corr$`-3` <- NA
corr$`-2` <- NA
corr$`-1` <- NA
corr$`0` <- NA
corr$`1` <- NA
corr$`2` <- NA
corr$`3` <- NA
  
x <- 1
  
for (corr1Id in 1:ncol(corr_temp)) {
    c1 = corr_temp[,corr1Id]

    for(corr2Id in 1:ncol(corr_temp)) {
      c2 = corr_temp[,corr2Id]
      correlation = ccf(c1, c2, lag.max = 3, 
                        na.action = na.contiguous,
                        plot=F)
      
      corr[x,3:9] <- correlation$acf %>% 
        as.data.frame() %>% t()
    
      x<- x+1
    }
}
```

```{r tv_ads: CCF long df}
# convert dataframe to long format
corrLong_tv_ads <- corr %>%
    gather(lag, ccf, `-3`:`3`) %>%
  mutate(lag = as.numeric(lag),
         type = "ads",
         sample = "program guides")
```

```{r tv_ads: Plot CCF}
# Calculate confidence intervals
ci_upper <- 2/sqrt(length(resid[,1]))
ci_lower <- -2/sqrt(length(resid[,1]))

corrLong_tv_ads %>%
  filter(Var1!=Var2) %>%
  ggplot(aes(lag,ccf,
             fill=Var1)) +
  geom_col(position = "dodge",
           #show.legend = F,
           alpha=0.8) +
  scale_fill_manual(values=col) +
  facet_wrap(~Var2, ncol=3)+
  scale_x_continuous(breaks = c(-3:3)) +
  scale_y_continuous(
    limits = c(-1,1),
    breaks = seq(-1,1,0.2)) +
  geom_hline(yintercept = ci_upper, 
             color = "black",
             size = 0.3,
             linetype = 2)+
  geom_hline(yintercept = ci_lower, 
             color = "black",
             size=0.3,
             linetype = 2)+
  labs(x="", fill="", caption = paste("Timespan:", min,"to", max)) +
  theme(legend.position = "bottom")

ggsave("../figs/ccf_ads_tv.png", width = 8, height = 6)
```

# 3. Women
```{r}
keep <- c("Brigitte", "freundin", "FÜR SIE")

min <- calculate_biweek(15, 2007)
max <- calculate_biweek(15, 2011)

women <- df %>%
  filter(Titel %in% keep) %>%
  mutate(date = calculate_biweek(issue, year))
```

```{r}
ggplot(women, aes(date, `Verkauf Gesamt`/1000,
                color=Titel)) +
  geom_line() +
  scale_color_manual(values = col[1:3]) +
  scale_x_date(date_breaks = "1 year", date_labels = "%Y") +
  labs(x="", color="", title = NULL, y="Sales in tsd.") +
  geom_vline(xintercept = as.numeric(min), linetype = "dashed", lwd=.5) +
  geom_vline(xintercept = as.numeric(max), linetype = "dashed", lwd=.5) +
  theme(legend.position="bottom")
  

ggsave('../figs/sales_women.png', width = 8, height = 6)
```

```{r}
ggplot(women, aes(date, `Anzeigen Gesamt`,
                color=Titel)) +
  geom_line() +
  scale_color_manual(values = col[1:3]) +
  labs(x="", color="", title = NULL, y="Total advertising pages") +
  scale_x_date(date_breaks = "years" , date_labels = "%Y") +
  geom_vline(xintercept = as.numeric(min), linetype = "dashed", lwd=.5) +
  geom_vline(xintercept = as.numeric(max), linetype = "dashed", lwd=.5) +
  theme(legend.position="bottom")

ggsave('../figs/ads_women.png', width = 8, height = 6)
```

## Sales
```{r women_sales: Create df}
women %>%
  dplyr::select(`Verkauf Gesamt`, date, Titel) %>%
  spread(Titel, `Verkauf Gesamt`) %>%
  filter(date >= as.Date(min)) %>%
  filter(date <= as.Date(max)) %>%
  dplyr::select(-date) -> tempdf
```
  
```{r women_sales: Calculate Arima}
results <- list()
mag <- names(tempdf)
x <- 1

for (i in mag) {
    selected <- tempdf[, -which(names(tempdf) == i)]
    xreg_matrix <- as.matrix(cbind(selected[,1],selected[,2]))
    temp <- auto.arima(tempdf[,i], xreg = xreg_matrix)
    
    results[[x]] <- temp
    x <- x+1
  }

resid <- cbind(results[[1]]$residuals, results[[2]]$residuals, results[[3]]$residuals)
```

```{r women_sales: Plot residuals}
autoplot(resid) +
  scale_color_manual(labels = mag, values = col[1:3]) +
  geom_hline(yintercept = 0, color = "grey50") +
  labs(y="residuals", x="", color = "",
       caption = paste("Timespan:", min,"to", max)) +
  theme(legend.position = "bottom")

ggsave("../figs/arima_sales_women.png", width = 8, height = 6)
```

```{r women_sales: Calculate CCF}
corr_temp <- resid %>% as.data.frame()
names(corr_temp) <- mag

# Create empty matrix
corr <- expand.grid(names(corr_temp), names(corr_temp))

corr$`-3` <- NA
corr$`-2` <- NA
corr$`-1` <- NA
corr$`0` <- NA
corr$`1` <- NA
corr$`2` <- NA
corr$`3` <- NA
  
x <- 1
  
for (corr1Id in 1:ncol(corr_temp)) {
    c1 = corr_temp[,corr1Id]

    for(corr2Id in 1:ncol(corr_temp)) {
      c2 = corr_temp[,corr2Id]
      correlation = ccf(c1, c2, lag.max = 3, 
                        na.action = na.contiguous,
                        plot=F)
      
      corr[x,3:9] <- correlation$acf %>% 
        as.data.frame() %>% t()
    
      x<- x+1
    }
}
```

```{r women_sales: CCF long df}
# convert dataframe to long format
corrLong_women_sales <- corr %>%
    gather(lag, ccf, `-3`:`3`) %>%
  mutate(lag = as.numeric(lag),
         type = "sales",
         sample = "women's magazines")
```


```{r women_sales: Plot CCF}
# Calculate confidence intervals
ci_upper <- 2/sqrt(length(resid[,1]))
ci_lower <- -2/sqrt(length(resid[,1]))

corrLong_women_sales %>%
  filter(Var1!=Var2) %>%
  ggplot(aes(lag,ccf,
             fill=Var1)) +
  geom_col(position = "dodge",
           #show.legend = F,
           alpha=0.8) +
  scale_fill_manual(values=col) +
  facet_wrap(~Var2, ncol=3)+
  scale_x_continuous(breaks = c(-3:3)) +
  scale_y_continuous(
    limits = c(-0.8,0.8),
    breaks = seq(-0.8,0.8,0.2)) +
  geom_hline(yintercept = ci_upper, 
             color = "black",
             size = 0.3,
             linetype = 2)+
  geom_hline(yintercept = ci_lower, 
             color = "black",
             size=0.3,
             linetype = 2)+
  labs(x="", fill="", caption = paste("Timespan:", min,"to", max)) +
  theme(legend.position = "bottom")

ggsave("../figs/ccf_sales_women.png", width = 8, height = 6)
```

## Advertising
```{r women_ads: Create df}
women %>%
  dplyr::select(`Anzeigen Gesamt`, date, Titel) %>%
  spread(Titel, `Anzeigen Gesamt`) %>%
  filter(date >= as.Date(min)) %>%
  filter(date <= as.Date(max)) %>%
  dplyr::select(-date) -> tempdf
```
  
```{r women_ads: Calculate Arima}
results <- list()
mag <- names(tempdf)
x <- 1

for (i in mag) {
    selected <- tempdf[, -which(names(tempdf) == i)]
    xreg_matrix <- as.matrix(cbind(selected[,1],selected[,2]))
    temp <- auto.arima(tempdf[,i], xreg = xreg_matrix)
    
    results[[x]] <- temp
    x <- x+1
  }

resid <- cbind(results[[1]]$residuals, results[[2]]$residuals, results[[3]]$residuals)
```

```{r women_ads: Plot residuals}
autoplot(resid) +
  scale_color_manual(labels = mag, values = col[1:3]) +
  geom_hline(yintercept = 0, color = "grey50") +
  labs(y="residuals", x="", color = "",
       caption = paste("Timespan:", min,"to", max)) +
  theme(legend.position = "bottom")

ggsave("../figs/arima_ads_women.png", width = 8, height = 6)
```

```{r women_ads: Calculate CCF}
corr_temp <- resid %>% as.data.frame()
names(corr_temp) <- mag

# Create empty matrix
corr <- expand.grid(names(corr_temp), names(corr_temp))

corr$`-3` <- NA
corr$`-2` <- NA
corr$`-1` <- NA
corr$`0` <- NA
corr$`1` <- NA
corr$`2` <- NA
corr$`3` <- NA
  
x <- 1
  
for (corr1Id in 1:ncol(corr_temp)) {
    c1 = corr_temp[,corr1Id]

    for(corr2Id in 1:ncol(corr_temp)) {
      c2 = corr_temp[,corr2Id]
      correlation = ccf(c1, c2, lag.max = 3, 
                        na.action = na.contiguous,
                        plot=F)
      
      corr[x,3:9] <- correlation$acf %>% 
        as.data.frame() %>% t()
    
      x<- x+1
    }
}
```

```{r women_ads: CCF long df}
# convert dataframe to long format
corrLong_women_ads <- corr %>%
    gather(lag, ccf, `-3`:`3`) %>%
  mutate(lag = as.numeric(lag),
         type = "ads",
         sample = "women's magazines")
```

```{r women_ads: Plot CCF}
# Calculate confidence intervals
ci_upper <- 2/sqrt(length(resid[,1]))
ci_lower <- -2/sqrt(length(resid[,1]))

corrLong_women_ads %>%
  filter(Var1!=Var2) %>%
  ggplot(aes(lag,ccf,
             fill=Var1)) +
  geom_col(position = "dodge",
           #show.legend = F,
           alpha=0.8) +
  scale_fill_manual(values=col) +
  facet_wrap(~Var2, ncol=3)+
  scale_x_continuous(breaks = c(-3:3)) +
  scale_y_continuous(
    limits = c(-1,1),
    breaks = seq(-1,1,0.2)) +
  geom_hline(yintercept = ci_upper, 
             color = "black",
             size = 0.3,
             linetype = 2)+
  geom_hline(yintercept = ci_lower, 
             color = "black",
             size=0.3,
             linetype = 2)+
  labs(x="", fill="", caption = paste("Timespan:", min,"to", max)) +
  theme(legend.position = "bottom")

ggsave("../figs/ccf_ads_women.png", width = 8, height = 6)
```

# 4. Combine all

```{r combine dfs}
corrLong_all <- rbind(corrLong_fss_sales1, corrLong_fss_sales2,
            corrLong_fss_ads1, corrLong_fss_ads2,
            corrLong_tv_sales, corrLong_tv_ads,
            corrLong_women_ads, corrLong_women_sales)
```

```{r}
df_wide <- df_combined %>% 
  filter(lag == 0) %>% 
  filter(Var1 != Var2) %>% 
  distinct(ccf, .keep_all = TRUE) %>%  
  mutate(magazine_pair = paste(Var1,"&", Var2)) %>% 
  dplyr::select(magazine_pair, ccf, type, sample) %>% 
  arrange(magazine_pair) %>% 
  spread(type, ccf) %>% 
  arrange(sample)
```

# TV & Women
```{r}
women <- c("Brigitte", "freundin", "FÜR SIE")
tv <- c("TV Movie", "TV Spielfilm", "TV Today")
keep <- c(women,tv)

min <- calculate_biweek(15, 2007)
max <- calculate_biweek(15, 2011)

tv_women <- df %>%
  filter(Titel %in% keep) %>%
  mutate(date = calculate_biweek(issue, year))
```

## Sales
```{r tv_women_sales: Create df}
tv_women %>%
  dplyr::select(`Verkauf Gesamt`, date, Titel) %>%
  spread(Titel, `Verkauf Gesamt`) %>%
  filter(date >= as.Date(min)) %>%
  filter(date <= as.Date(max)) %>%
  dplyr::select(-date) -> tempdf
```
  
```{r tv_women_sales: Calculate Arima}
# FIXME: calculcate ARIMA for different constelations

results <- list()
x <- 1

for (i in women) {
    selected <- tempdf[, tv]
    xreg_matrix <- as.matrix(cbind(selected[,1],selected[,2],selected[,3]))
    temp <- auto.arima(tempdf[,i], xreg = xreg_matrix)
    
    results[[i]] <- temp
    x <- x+1
}

resid <- cbind(results[[1]]$residuals, results[[2]]$residuals, results[[3]]$residuals)
```

```{r tv_women_sales: Calculate CCF}
# FIXME: calculcate ARIMA cross-correlation
corr_temp <- resid %>% as.data.frame()
names(corr_temp) <- women

# Create empty matrix
corr <- expand.grid(names(corr_temp), tv)

corr$`-3` <- NA
corr$`-2` <- NA
corr$`-1` <- NA
corr$`0` <- NA
corr$`1` <- NA
corr$`2` <- NA
corr$`3` <- NA
  
x <- 1
  
for (corr1Id in 1:ncol(corr_temp)) {
    c1 = corr_temp[,corr1Id]

    for(corr2Id in 1:ncol(corr_temp)) {
      c2 = corr_temp[,corr2Id]
      correlation = ccf(c1, c2, lag.max = 3, 
                        na.action = na.contiguous,
                        plot=F)
      
      corr[x,3:9] <- correlation$acf %>% 
        as.data.frame() %>% t()
    
      x<- x+1
    }
}

```

```{r tv_women_sales: CCF long df}
# convert dataframe to long format
corrLong_tv_women_sales <- corr %>%
    gather(lag, ccf, `-3`:`3`) %>%
  mutate(lag = as.numeric(lag))
```


```{r tv_women_sales: Plot CCF}
# Calculate confidence intervals
ci_upper <- 2/sqrt(length(resid[,1]))
ci_lower <- -2/sqrt(length(resid[,1]))

corrLong_tv_women_sales %>% 
  ggplot(aes(lag,ccf,
             fill=Var2)) +
  geom_col(position = "dodge",
           #show.legend = F,
           alpha=0.8) +
  scale_fill_manual(values=col) +
  facet_wrap(~Var1, ncol=3) +
  scale_x_continuous(breaks = c(-3:3)) +
  # scale_y_continuous(
  #   limits = c(-0.8,0.8),
  #   breaks = seq(-0.8,0.8,0.2)) +
  geom_hline(yintercept = ci_upper, 
             color = "black",
             size = 0.3,
             linetype = 2)+
  geom_hline(yintercept = ci_lower, 
             color = "black",
             size=0.3,
             linetype = 2)+
  labs(x="", fill="", caption = paste("Timespan:", min,"to", max)) +
  theme(legend.position = "bottom")

#ggsave("../figs/ccf_sales_tv_women.png", width = 8, height = 6)
```
